%%This is a very basic article template.
%%There is just one section and two subsections.
% \documentclass{article}
%\documentclass[phd,ilcc,twoside]{infthesis}
\documentclass[bsc,logo, abbrevs]{infthesis}
\project{\textbf{Supervisor}: Dr Ewan Klein}

% This package is for times font
\usepackage{times}

% Adjust tables
\usepackage{adjustbox}

% This package is for Informatics thesis style
\usepackage{eushield}

% This package is for your references
\usepackage[numbers]{natbib}

% This package is for figures
\usepackage{graphicx}

% This package is for urls
\usepackage{url}

%Prevents placing floats before a section.
\usepackage[section]{placeins}

% Degree command
\usepackage{gensymb}

% For symbols and equations 
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{acronym}

% Images below text

\usepackage{float}

% Using urls

\usepackage{url}

%Wrap text around figures

\usepackage{wrapfig}

%Euro symbol

\usepackage{eurosym}

%verbatim color

\usepackage{fancyvrb,xcolor}

%verbatim break lines

\usepackage{spverbatim}

% Referencing in center
\usepackage{csquotes}
\renewcommand{\mkbegdispquote}[2]{\itshape}

% Tables with fixed width

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}


% Micrometer symbol

\usepackage{siunitx}

% Quotes 

\newcommand{\quotes}[1]{``#1''}


%% Information about the title, etc.
\title{AirQueue: \protect\\ A Personal Mobile Application to Visualise Air Quality in Scotland}
\author{Alberto Vazquez Martinez}

%% Specify the abstract here.
\abstract{

As air quality over the world becomes crucial for the environmental agenda, new air quality monitoring sensors are being developed and deployed. The gathered data is vaster, more dynamic and coarse-grained than ever before. However, current approaches to disseminating it often fail on being useful, intuitive and personal enough to serve as a decision support tool for people concerned with the quality of the air they breathe. This thesis explores the current approaches used for air quality visualisation as well as the available data sources and technologies to identify how can be improved to be more useful for people. The aim of this dissertation project is to analyse, develop and implement a mobile application to serve such a purpose by taking into account the final users as designers and stakeholders.

}

\begin{document}

%% First, the preliminary pages
\begin{preliminary}

\maketitle
\begin{acknowledgements}

I express my sincere gratitude to my supervisor Dr Ewan Klein for his excellent advice and guidance throughout the project. Without his constant motivation the project would never end up as it did.
Many thanks as well to Catherine Magil for all the time and advice offered. Also, my sincere gratitude to everyone from the Asthma UK Group for the time offered to enlighten the project. Similarly I would like to thank my sponsor institution CONACYT for the finantial 
Finally, I would like to thank the continuous support of my family, that despite the distance have always been by my side.

\end{acknowledgements}

%% Create the table of contents
\standarddeclaration
%%\dedication{Acknowledgements}

\tableofcontents
\listoffigures
\iffalse
\listoftables
\begin{accron}\input{acronyms}\end{accron}
\fi
\end{preliminary}

\include{1-introduction/0-Chapter-Introduction}
\include{2-background/0-Chapter-Background}
\include{3-methodology/0-Chapter-Methodology}
\include{4-analysis/0-Chapter-Analysis}
\include{5-design/0-Chapter-Design}
\include{6-implementation/0-Chapter-Implementation}
\include{7-evaluation/0-Chapter-Evaluation}
\include{8-conclusion/0-Chapter-Conclusion}


\bibliography{mendeley}
\bibliographystyle{IEEEtranN}
\appendix
\include{appendix1}


\end{document}
