\section{Dissertation Outline}
This dissertation is structured as follows: 
 
\bigskip
 Chapter 2: Background
\bigskip

This chapter discusses relevant background topics key to understanding the dissertation. It explains the project's importance in the context of the pollution problem, including definitions to follow the basic air quality dissemination terms and related health issues. Past approaches for visualising are also discussed and critically evaluated, as well as explaining in detail what is meant by data visualisation and how to achieve it from a decision support perspective.
 
\bigskip
 Chapter 3: Methodology
\bigskip
  
This chapter describes the methodology and processes that have been used throughout the project. It describes how the development was addressed not only from a human-computer interaction perspective but as well from a software engineering perspective. 
  
\bigskip  
 Chapter 4: Analysis and Design
\bigskip

The analysis and design of the system are  both addressed in this chapter. A detailed analysis of the current needs of a new air quality application is presented, as well as explaining the design and infrastructure choices made for achieving the project goal in a way all stakeholders are considered. The first application prototype is presented.
 
\bigskip
Chapter 5: Implementation
\bigskip

This chapter describes how the required infrastructure and software components were set-up to proceed with the implementation of the final two prototypes, as well as the transitional choices that resulted from the user-centred development approach.

\bigskip
 Chapter 6: Evaluation
\bigskip

The final technical and user evaluations are presented in this chapter by describing how well the defined requirements in Chapter 4 were met with quantitative and qualitative methods.

\bigskip
 Chapter 7: Conclusion
\bigskip

This chapter looks at the aims of the dissertation from an integrative perspective highlighting what has been accomplished so far and giving recommendations for future research.